Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-07-21 vita.tex
more vita (hand crafted rather than bibtex :/)

%\begin{tabular}{@{\hspace{0.2in}}@{\hspace{0.2in}}p{4.5in}}
\begin{tabular}{p{1.5in}p{6in}}
NAME: & Joel Adam Berger \\
\\
EDUCATION: & B.S., Physics, University of Illinois at Chicago,\\
& Chicago, Illinois, 2005 \\
\\
TEACHING: & Something here\\
\\
PROFESSIONAL MEMBERSHIPS: & Microscopy Society of America\\
& Midwest Microscopy and Microanalysis Society\\
\\
SELECTED \nobreak{PUBLICATIONS:} &\\
\end{tabular}

>>>>

%\begin{tabular}{@{\hspace{0.2in}}@{\hspace{0.2in}}p{4.5in}}
\begin{tabular}{p{1.5in}p{4in}}
NAME: & Joel Adam Berger \\
\\
EDUCATION: & B.S., Physics, University of Illinois at Chicago,\\
& Chicago, Illinois, 2005 \\
\\
TEACHING: & \LaTeX{} for Technical Publishing (PHYS491 - Spring 2011)\\
\\
& Problem-Solving Workshop for General Physics II (Electricity and Magnetism), General Physics II (Electricity and Magnetism) Lab, General Physics I (Mechanics)\\
\\
PROFESSIONAL MEMBERSHIPS: & Microscopy Society of America\\
& Midwest Microscopy and Microanalysis Society\\
\\
SELECTED \nobreak{PUBLICATIONS:}
& Berger, J. A., Greco, M. J., and Schroeder, W. A.: High-power, femtosecond, thermal-lens-shaped Yb:KGW oscillator. \uline{Opt. Express}, 16(12), 2008.\\
\\
& Berger, J. A., Hogan, J. T., Greco, M. J., Schroeder, W. A., Nicholls, A. W., and Browning, N. D.: DC photoelectron gun parameters for ultrafast electron microscopy. \uline{Microsc. Microanal.}, 15(04), 2009.\\
\\
& Berger, J. and Schroeder, W.: Semianalytic model of electron pulse propagation: Magnetic lenses and rf pulse compression cavities. \uline{Journal of Applied Physics}, 108(12):124905, 2010.\\
\\
& Berger, J. A., Rickman, B. L., Li, T., Nicholls, A. W., and Schroeder, W. A.: Excited-state thermionic emission in III-antimonides: Low emittance ultrafast photocathodes. \uline{Applied Physics Letters}, 101(19):194103, 2012.\\
\end{tabular}
